State and Parameter Estimation for a Spatio-temporal Neural Fields

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
updates to artical

\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{Omega}\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top} 

@@

\begin{proof}

@@

&=&\mathbf{\Gamma}^{-1}\iint\limits_{\Omega} \boldsymbol{\phi}\left(\mathbf{r}\right) \mathbf E[e_t\left(\mathbf{r}\right)e_t\left(\mathbf{r}'\right)]\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
&=&\mathbf{\Gamma}^{-1}\iint\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top} 

@@

\end{proof}

>>>>

\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \beta\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top} 

@@

\subsection{proof}

@@

&=&\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega} \boldsymbol{\phi}\left(\mathbf{r}\right) \mathbf E[e_t\left(\mathbf{r}\right)e_t\left(\mathbf{r}'\right)]\boldsymbol{\phi}\left(\mathbf{r}'\right)^{\top}d\mathbf{r}' d\mathbf r\mathbf{\Gamma}^{- \top} \nonumber\\
&=&\mathbf{\Gamma}^{-1}\int\int\limits_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top} 

@@

% \end{proof}
\section{Parameter estimation using LS}
 \mathbf x_{t+1}=\mathbf{x}_{t}+T_s \mathbf{Q}(\mathbf{x}_t)\boldsymbol{\theta}-\alpha T_s\mathbf{x}_t+T_s\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\varepsilon_t(\mathbf r)d\mathbf r
\label{eq:statespacemodel}
where the matrix $\mathbf Q_{n_x \times n_{\boldsymbol{\theta}}}(\mathbf x_t)$ is defined as
 Q_{n_x \times n_{\boldsymbol{\theta}}}=\Gamma^{-1}\int_\Omega\boldsymbol{\phi}(\mathbf r)\int_\Omega f(\boldsymbol{\phi}^\top(\mathbf r')\mathbf x_t)\mathbf{\psi}^\top(\mathbf r-\mathbf r')d\mathbf r'd\mathbf r
and $T_s$ is the sampling period. Least Square method can be used as (\ref{eq:statespacemodel}) is linear in parameters. At each time instant we have
 \mathbf x_{1}&=&\mathbf x_{0}+T_s \mathbf Q(\mathbf x_0) \boldsymbol{\theta}-\alpha T_s\mathbf x_0+T_s\mathbf e_0 \nonumber \\
 \mathbf x_{2}&=&\mathbf x_{1}+T_s \mathbf Q(\mathbf x_1) \boldsymbol{\theta}-\alpha T_s\mathbf x_1+T_s\mathbf e_1\nonumber\\
&\vdots& \nonumber\\
 \mathbf x_{n}&=&\mathbf x_{n-1}+T_s \mathbf Q(\mathbf x_{n-1}) \boldsymbol{\theta}-\alpha T_s\mathbf x_{n-1}+T_s\mathbf e_{n-1}
in matrix form
 \left[\begin{array}{{cccc}} \mathbf x_{1}\\\mathbf x_{2}\\\vdots\\\mathbf x_{n}\end{array}\right]
	-\left[\begin{array}{cccc} \mathbf x_{0}\\\mathbf x_{1}\\\vdots\\\mathbf x_{n-1}\end{array}\right]
	=T_s\left[\begin{array}{cc}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{array}\right]
	\left[\begin{array}{cc} \boldsymbol{\theta} \\ \alpha\end{array}\right]+T_s
		\left[\begin{array}{cccc}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{array}\right]
or in compact form we have
 \mathbf Z=\mathbf X \mathbf W+\boldsymbol \xi
where
 \mathbf Z=\left[\begin{array}{cccc} \mathbf x_{1}-\mathbf x_{0}\\
\mathbf x_{2}-\mathbf x_{1}\\\vdots\\
\mathbf x_{n}-\mathbf x_{n-1}\end{array}\right],\quad \mathbf X=T_s\left[\begin{array}{cccc}\mathbf Q(\mathbf x_0)&-\mathbf x_{0}\\
\mathbf Q(\mathbf x_1)&-\mathbf x_{1}\\\vdots\\ \mathbf Q(\mathbf x_{n-1})&-\mathbf x_{n-1}\end{array}\right]
,\quad \mathbf W=\left[\begin{array}{cc} \boldsymbol{\theta} \\ \alpha\end{array}\right],\quad \boldsymbol \xi=T_s\left[\begin{array}{cccc}\mathbf e_0\\\mathbf e_1\\\vdots\\\mathbf e_{n-1}\end{array}\right]
using the method of Least Square $ \mathbf W$ can be estimated
 \mathbf W\approx(\mathbf X^\top\mathbf X)^{-1}\mathbf X^\top\mathbf Z
